Title

### 2023-06-05 main.tex
Cambios intro y angulos

\begin{flushleft}
{\Large
\textbf\newline{Title of submission to PLOS journals} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Tomás Basile\textsuperscript{1\Yinyang},
Carlos Pineda\textsuperscript{2*\Yinyang},
\\
\bigskip
\textbf{1} Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico
\\
\textbf{2} Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México
\\
\bigskip

@@

% Use "Eq" instead of "Equation" for equation citations.
% }}}
\section{Introduction} % {{{
\tbnote{versión muy preliminar de la intro, para ir teniendo algo escrito de una vez. }\\

@@

In this article, our primary objective is to present a 
quantum algorithm capable of simulating Pauli channels on quantum computers, 
and we demonstrate its implementation using IBM's quantum computers. 
This algorithm is designed to simulate any Pauli channel on a system of $N$ qubits,
and works by utilizing $2N$ ancilla qubits.

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
which are defined as a continuous parametrization of
$N$-qubit Pauli channels. 
Consequently, we adapt the algorithm developed for Pauli channels 
to accommodate these dynamical maps by employing a 
parametrized quantum circuit, that is, 
a quantum circuit in which some of the
 operations depend on a variable parameter~\cite{cerezo}.

The investigation of parametrized quantum
circuits holds extensive importance, 
as they find applications in quantum machine learning~\cite{Benedetti}
and describe general quantum transformations dependent on a parameter. Substantial research has been 
devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}. 
In this article, we contribute to this body of work by establishing theorem \ref{theorem2},
which outlines the types of transformations that 
can be done using a parametrized quantum with the condition that only one
 single-qubit operation in the circuit may depend on the parameter. 
We explicitly find the mathematical conditions for these types of
transformations and conclude about which 
Pauli dynamical maps can be done with them.

% }}}
\section{Pauli channels and dynamical maps}  \label{sec: Pauli Channels} % {{{
% Intro  {{{
% \textbf{Lista de puntos:}
% \begin{itemize}
% \item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
% \item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
% \item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
% \end{itemize}

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
\arctan(\sqrt{k_{11}/k_{10}}),
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}}),
\label{eq:angle2} \\
\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
\arctan(\sqrt{k_{11}/k_{10}}).
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Quisiera ver las ecuaciones sin la teheta despejada. Por ejemplo la de theta 1
es $\cos^2 (\theta_1/2) = k00 + k01$ bueno mas bonita, pero asi. Luego las de tehta0 y theta2 
quizá tambien sean sencillas. Las quiero ver!!!}
\tbnote{Ah, ya entiendo. Las única forma que veo de escribirlas es:
\begin{align*}
\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10} }}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }} \\
\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10} }}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }}
\end{align*}
No veo cómo escribir ecuaciones de las thetas no despejadas que sean sencillas.
}

\tbnote{Obteniendo el seno y coseno de estos ángulos tampoco se 
consigue algo mucho mejor:
\begin{align*}
\cos \theta_0 = \dfrac{\sqrt{k_{00} k_{10}} + \sqrt{k_{01} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}} \\
\sin \theta_0 =  \dfrac{\sqrt{k_{01} k_{10}} - \sqrt{k_{00} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}}  \\
\cos \theta_2 = \sqrt{\dfrac{k_{00}k_{10}}{(k_{00}+k_{01})(k_{10}+k_{11})}} \left( -1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right) \\
\sin \theta_2 =  - \sqrt{\dfrac{k_{00}k_{10} + k_{01}k_{11} - 2 \sqrt{k_{00} k_{01} k_{10} k_{11}}}{(k_{00} + k_{01}) (k_{10} + k_{11})}} \left(\sqrt{\dfrac{k_{01}}{k_{00}}} + \sqrt{\dfrac{k_{11}}{k_{10}}} \right) \left(-1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right)^{-1}
\end{align*}
Probé combinar estas cantidades de diferentes formas, pero ninguna se simplificaba.}

>>>>

\begin{flushleft}
{\Large
\textbf\newline{Title of submission to PLOS journals} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Tomás Basile\textsuperscript{1,2\Yinyang},
Carlos Pineda\textsuperscript{2*\Yinyang},
\\
\bigskip
\textbf{1} Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico
\\
\textbf{2} Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México
\\
\bigskip

@@

% Use "Eq" instead of "Equation" for equation citations.
% }}}
\section{Introduction} % {{{

Puntos hechos en el artículo:
\begin{itemize}
\item Propuesta de algoritmo para canal es de Pauli de N qubits y su simulación en compus cuánticas
\item Condiciones para que un circuito parametrizado use una sola rotación parametrizada. En particular luego aplicadas al algoritmo para mapas dinámicos de Pauli.
\end{itemize}

\tbnote{versión muy preliminar de la intro, para ir teniendo algo escrito de una vez. }\\

@@

On the other hand, we shall also work with parametrized quantum circuits, that is,  
a quantum circuit in which some of the operations depend on a variable parameter~\cite{cerezo}. 
The investigation of parametrized quantum
circuits holds extensive importance, 
as they find applications in quantum machine learning~\cite{Benedetti}
and describe general quantum transformations dependent on a parameter. Substantial research has been 
devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.

In this article, our first objective is to present a 
quantum algorithm capable of simulating Pauli channels on quantum computers, 
and we demonstrate its implementation using IBM's quantum computers. 
This algorithm is designed to simulate any Pauli channel on a system of $N$ qubits,
and works by utilizing $2N$ ancilla qubits.

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
which are defined as a continuous parametrization of
$N$-qubit Pauli channels. 
Consequently, we adapt the algorithm developed for Pauli channels 
to accommodate these dynamical maps by employing a 
parametrized quantum circuit. 
We contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2}.
This theorem outlines the types of transformations that 
can be done using a parametrized quantum circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
We explicitly find the mathematical conditions for these types of
transformations and conclude about which 
Pauli dynamical maps can be done with them.

The paper is organized as follows: In section \ref{sec: Pauli Channels} 
we give the definition of quantum channels and focus particularly on Pauli channels for systems of
$N$ qubits. 
In section \ref{sec: Circuit for a Pauli Channel} we show the proposed circuit 
to implement a Pauli channel of $N$ qubits in a quantum computer. 
Furthermore, we simulate it on IBM’s computers for the special case of $N=1$
and obtain the fidelity of this implementation.  
In section \ref{sec: 1PR Circuits} we shift our focus to parametrized quantum circuits with the goal of
generalizing the circuit for Pauli channels to one for Pauli dynamical maps. 
We introduce theorem \ref{theorem2} to establish what operations can be done with a 
parametrized circuit that uses only one single-qubit operation dependent on the parameter.
Finally, in section \ref{sec: 1PR circuit for a Pauli map} 
we apply this theorem for the circuit of Pauli dynamical
maps and show a couple of maps that fulfill the theorem's conditions.

% }}}
\section{Pauli channels and dynamical maps}  \label{sec: Pauli Channels} % {{{

% Intro  {{{
% \textbf{Lista de puntos:}
% \begin{itemize}
% \item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
% \item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
% \item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
% \end{itemize}

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
\arctan(\sqrt{k_{11}/k_{10}}),
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}}),
\label{eq:angle2} \\
\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
\arctan(\sqrt{k_{11}/k_{10}}).
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Quisiera ver las ecuaciones sin la teheta despejada. Por ejemplo la de theta 1
es $\cos^2 (\theta_1/2) = k00 + k01$ bueno mas bonita, pero asi. Luego las de tehta0 y theta2 
quizá tambien sean sencillas. Las quiero ver!!!}
%\tbnote{Ah, ya entiendo. Las única forma que veo de escribirlas es:
%\begin{align*}
%\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10} }}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }} \\
%\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10} }}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }}
%\end{align*}
%No veo cómo escribir ecuaciones de las thetas no despejadas que sean sencillas.
%}

%\tbnote{Obteniendo el seno y coseno de estos ángulos tampoco se 
%consigue algo mucho mejor:
%\begin{align*}
%\cos \theta_0 = \dfrac{\sqrt{k_{00} k_{10}} + \sqrt{k_{01} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}} \\
%\sin \theta_0 =  \dfrac{\sqrt{k_{01} k_{10}} - \sqrt{k_{00} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}}  \\
%\cos \theta_2 = \sqrt{\dfrac{k_{00}k_{10}}{(k_{00}+k_{01})(k_{10}+k_{11})}} \left( -1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right) \\
%\sin \theta_2 =  - \sqrt{\dfrac{k_{00}k_{10} + k_{01}k_{11} - 2 \sqrt{k_{00} k_{01} k_{10} k_{11}}}{(k_{00} + k_{01}) (k_{10} + k_{11})}} \left(\sqrt{\dfrac{k_{01}}{k_{00}}} + \sqrt{\dfrac{k_{11}}{k_{10}}} \right) \left(-1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right)^{-1}
%\end{align*}
%Probé combinar estas cantidades de diferentes formas, pero ninguna se simplificaba.}

\tbnote{Creo que la mejor forma es la siguiente (nota:
intercambié los ángulos 0 y 1 en la imagen para que 1 y 2
sean los que van juntos y el 0 por separado, en lugar de que los juntos sean el 0 y 2) :}
\tbnote{of angles defined by the following equations:
\begin{align*}
\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}}\\
\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}} \\
\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}
\end{align*}
También podría quitar los factores de 2 que hay aquí y meter factores de 2 en los ángulos del circuito.
}
